\chapter{Death}

Death is a big change, though it is also a release, and a reuniting with the
higher self. 

Host-bodies are precious commodities, and should
be treated with the utmost respect. As a soul you are in a sense borrowing a
piece of the galaxy cosmos for a time to use as a vessel/body. You are
replenishing it regularly, and it is being remade as well, as old cells die and
are replaced by new ones. 

Nevertheless host-bodies grow old, as do mind-states, and so are shed
occasionally to allow our souls to have new experiences. 

Just like a computer can get old and defective, so too can the software that
runs on that computer,  simply from a large number of upgrades and shudowns, and
idiosyncratic configurations which may leave the mind in an inconsistent and not
very functional state. At this point IT people often do a reinstall, or a
restore from a working state. 

\subsection{Suicide}

Suicide is heavily discouraged. There is often a form of punishment for those
that commit suicide, where one has to sit in a sphere of possibility, and be
guided through all the other scenarios that could have led to better outcomes. 

The one exception seems to be when there is a major host-body failure that
causes extreme chronic pain that can't be remedied. In such an extreme case, it
seems the soul world is rather understanding. 

Often enough suicidial feelings can be remedied, by good nutrition and exercise. 
For instance EPA a form of Omega-3 has been clinically shown to be equivalent to
an anti-depressant, with no side-effects, as essentially it is providing
essential fatty-acids to help your brain and heart function more effectively. 

For those that have tried everything else to feel better, and they have nothing
left to live for, despite having wealth/healht/connections there is still 
another way. While perhaps for your soul, there is nothing to gain from this
vehicle, there may be for another.

It is known as Trong-Jug in Buddhism, though the focus is typically on the soul 
adopting another body, wheras here the focus is on giving a body, up for 
adoption.  

The basic idea is to think about, or ideally write out, what kind of soul you
would be willing to take the reigns of your body. May be a good idea to make
some restrictions, like that they will be gentle and kind to your friends and
family, that they will take good care of the body, and that they will make a
meaningful beneficial contribution to society. 

Certainly don't want it to be too limiting, such as by saying, only a high level
lama, since then may be up for adoption for a long time, before one comes along
that meets the criteria. 

Though basically after writing it out, it is a good idea to maintain good
health, finances and all that. You'll probably have to confirm your intent
several times telepathically. Within perhaps a few months or years depending on
how healthy your body and environment is, you may lay down for a meditation, and
find that a soul swap is available, you'll be able to leave the body, and the
new soul will take over. Making it a win-win-win situation, for you, the new
soul, and the friends and family that don't have to go through a funeral. 



