\documentclass{report}
\usepackage{green_buddhism}
\title{Green Buddhism: A Programmer's Religion}
%\subtitle{Enjoying a life of liberty}
\author{Logan Streondj elspru@zeroid.bit}
\begin{document}
\section{recent reform}
\begin{itemize}
  \item added What is the story of Green Buddhism? (\ref{whatstory}) 2016/10/29
  \item added grey population distribution subsection (\ref{popdist})
2016/10/28
 \item updated Arecibo section (\ref{arecibo}) 2016/10/28
 \item added bibilography (\ref{bibliography}) 2016/10/28
\end{itemize}

\tableofcontents
\part{Galaxy Domain Strategy}

\chapter{What is the story of Green Buddhism?}
\label{whatstory}
In 2009 I went to Thailand to be a monk for a month. I liked the robes but they
said I couldn't wear them when I got back to Canada, unless I was a monk at one
of their temples. However when I asked if I could remake them into a different 
colour, like green or purple and then wear them, they said sure. 

The robe style has been around for thousands of years, and is used by a variety
of different faiths in Asia. 

Also while I was in Thailand, I was somewhat disenchanted, or even frightened by
the blatant disregard for nature. When I asked to go to a park, the only
greenspace in the town of Fang, was the cemetery. 

I returned to Canada and turned to gardening, and earth-based religion for a
while. 

Earlier, in 2006, I was doing a hermitage in my parents basement. Only writing
my thoughts and meditating for a year, with minimal contact with the outside
world. I achieved many deep states of meditation.  

One of which was that of emptiness, a delta brainwave meditation. 
I came to a certain understanding of nothingness, and the origin of the
cosmos (\ref{origination}).

The profound realization of my awakening, is that truth is personal, and that
reality is mutual. When attempting to explain it to someone, they said it was
the basis for a religion. 

Indeed it has been. To define a word, one could make a dictionary entry. Though
I decided to go the path of creating a human speakable programming language.
Humans having liquid minds, which  may flow into other definitions. Once a word
is defined in computer programming, it can be a foundation of a whole genus of
minds, solid as can be.  

In addition to my vision of the origins of the cosmos, and profound
realizations, I also had many visions of my past lives. Of course they are only
my truth, so you don't have to believe them, to you they are only imaginary
stories. 

In my alleged past lives, I've traveled between galaxies, and reincarnated in a
great variety of solid, liquid and even gaseus bodies. My vision, is to see the
co-operation of all. So we may all live with safety, health, socializing, and
liberty. 

\input{origination}

\input{history}

\input{mission_activity}

%\chapter{Mission Feasiblity}

To be continued.
Check back for more.


\end{document}
