\documentclass{report}
\usepackage{green_buddhism}
\begin{document}
\chapter{Introduction}
Here you will learn, some secrets of the cosmos.

If  you can forgive me for being who I am, then you can probably forgive anyone,
including yourself. 

Herein you will learn about the
\begin{itemize}
  \item Creativity of Emptiness
  \item Soul World
  \item Life mission
  \item Accessing subconscious mind
  \item Galactic history
  \item Robot host bodies
\end{itemize}

Some are based on science, some on meditation, some on memory. 
Later this will be a book, but for now here are some basics. 

\subsection{Why Buddhism?}
Buddhism was chosen because it is the most compatible with science.

Also Mahayanna Buddhism, Vajrayana Buddhism (which we'll call Bodhisattva
Buddhism for brevity) and beyond have a Bodhisattva 
precept which disallows schisms.  So the various traditions of `Bodhisattva'
Buddhisms are schools, 
and they get along. We are all incarnating to learn, and more perspectives only
enrich the educational experience.

\subsection{How is this Buddhism?}

While this book is not a reiteration of past Buddhist teachings, it includes
them. So unless otherwise noted it has all the same features as any Bodhisattva
Buddhist tradition.  

For example, to become a Buddhist one only needs to take refuge in the three
jewels.  

\begin{itemize}
  \item I take refuge in the Buddha (awakened mind)
  \item I take refuge in the Dharma (teachings)
  \item I take refuge in the Sangha (community of meditators)
\end{itemize}

Daily solitary meditation is encouraged, as is attending regular group
meditation.

The teachings in this book are meant as suplementary material for your
practice. 

\subsection{Disclaimer} 
If these secrets are in conflict with your ideology,
then please see this as an imaginary story. 

\end{document}
