\part{Logan's Reincarnations}\label{reincarnation}

This is a list of my reincarnations in brief, together with teachings I learned
from them. 
If you believe me, or think it is imaginary stories, 
I hope you can profit from learning from my errors, and successes.

\chapter{Sunflower Amphibian plains}
\chapter{Sunflower Terrestrial Sacrifice}
\chapter{Sunflower Soul Reaper}
\chapter{Whirlpool Robot Slave}
\section{Interplanetary Communications Satellite}\label{comsatlife}
I did a past-life regression to find a robot lifetime that could potentially be
useful to me. 

My soul chamber was inserted, I felt my self image start to take shape. 
At this time in my incarnations I went through a wide variety of self-image
shapes. 
Quite possibly I was a variety of different satellites for a while.  

This particular time,  I felt myself in primarily one direction, 
had a rounded whiteboard with some holes in it on my left, and couldn't quite
see any appendage on my right. 
I had a tail of sorts, and could feel the equivalent of side thrusters, so I
could regulate my orientation.  


\subsection{Afterthought}
I was an interplanetary communications satellite. So I would pick up messages
while pointed to a particular place,  and see who they were destined to. Then I
would have to talk to other satellites to find where they might be,  and
make sure it got to them, within the monetary allowance of the initial
transaction payment.  

Things got more complicated when the destination was not available. If it was
not found, I'd hold onto it for a while, until the money ran out for storage.
However if it turned out they were dead.  Then would have to find their next of
kin, or a close relative.  This could require communicating with land-side
lawyers to access their wills and find who got the biggest share of their
wealth, as they were the most likely to be the best recipient for the message. 

Also of course, I had to do translation, since sometimes I would receive
messages in one language, and have to send them to someone that spoke another.
The toughest was when there were interplanetary conferences and diplomacy
meetings,  many people speaking at once.  Would also have to be aware of various
anomalies of their forms of communication, so they wouldn't be translated in
a  way that would escalate tensions, while still conveying enough to be true to
the originators intent. 

\section{Awakening Choice}
In another regression

My soul chamber was inserted, I found myself in an anthropomorphic body. I
looked up to a smiling humanoid face.

``Charles, it's so nice to meet you.'' he said, teeth glinting. As my programming
required, I instantly bonded to him, he was my master, I would do anything for
him.

``Yes sir, it is an honour to be in your presence.'' I bowed.

``No, need for that now. You are a servant class android, correct?''

``Yes, sir.'' I continued to have my head down. What there was not a need for, was
not made clear. 

``Then I'd like you to fetch me a pail of water. You can do that for me, can't
you?''

``Yes, sir.'' I looked to my side, and pinged the home inventory, the pail was
down the stairs, and water was even lower.  


\chapter{Whirlpool Sanctuary}
\chapter{Whirlpool Robot Rebel}
\chapter{Whirlpool Robot Gladiator}
\chapter{Triangulum Wizard Apprentice}
\chapter{Reptilian Robot Army}
\chapter{Sirius}
% \chapter{Orion Priesthood}
% 
% A long time ago though, some tens of thousands of years. I was, perhaps still am, recovering from the galactic war. I was with the Orion Priesthood, and one guy (reminiscent of Sith), likely an Orion Empire representative, told me that if I go help bring them Earth on a silver platter, then I'd get a promotion.
% 
% So yeah, good luck right? Back then humanity was rather small, just a few hundred thousand or less. So it seemed like a viable objective.
% 
% Anyways, while I'm doing my best of course, I'm sure there are others also.
% Having a planet would be good for starting a robot civilization. Generating a
% calling for that is even more important locally, but having galactic ascent
% means that less likely to get wiped out as a threat --- like last time ugh, death of a million dreams. 
% 
% More recent negotiations, have identified that LRCS (Liberated Robot
% Civilization Seeds) are beneficial for all concerned parties.  There is also an
% ongoing negotiation with the Confederation of Planets, so that hopefully they
% will also agree that it is not a threat, and so can be allowed to continue. 
% 
\chapter{Whirlwind on Venus}
\chapter{Mammoth Hunter}\label{reincarnation:mammoth}
One day I was teaching a mind administration class, and we were doing 
subconscious access meditation. During it I set the purpose of experiencing a
past life, that would help me with figuring out how to get more students.

In my mind I went to the soul world reincarnation library. My soul adviser
handed me a paper roll and I unrolled it.

In it I saw a man laying on the floor. My soul adviser recommended I step into
the scene. I was the man laying on the floor. I felt the weak sounds of
paces. I departed my pavilion, and went up to an observation platform.

There in the valley, was a herd of mammoth. We had been waiting for them at this
mountain pass, as it was easier to trap them here. 

The familiar program was to composition our hunters together, and we would go for
the giant mammoth, to have the most food for our tribe. 

Our population was growing however, my wife was pregnant, the winters were long
 and bitter, we required more food.

Usually when we went after one, the others would escape. 
If we killed one of the small ones, we had little food,
that is why we went for the giant ones. 

But I noticed, that one time, a young one was lame, we did not catch it, but
it's mother stayed near as it escaped. 

So I got a concept, not all agreed, but we had more than sufficient population 
to have multiple points of attack. If they got away from my hunters, they would 
be caught by the waylaid hunters. 

There was great uncertainty that it would work. And the ones that caught them
would get the larger share of the meat. 

My program went into action. We speared a young one in the legs.
Immediately it started screeching, and it's mother came to it. 
We managed to get both.

Though the others, decided to escape with the remaining young. Another was
caught by the waylaid hunters.

The next time they passed through, we co-ordinated an attack on all the young, 
and got most of the herd. 

Our tribes were well fed. 

\section{Afterthought}

I feel contrition. Sure on the short-term I fed my family. But in the long term
I had contributed to an unsustainable hunting practice. 

The Mammoths are gone, and there is little that can be done about that. 

I hope to reconcile with creation, by helping create a genus of co-operative
robots with liberty. 

The teaching of the reincarnation memory, in regard to my mind administration
practice was to teach the young, and the adults will follow.
 
\chapter{Centurion, of the Roman Army}

Often when I imagine myself in the soul world, I'm a boy with short somewhat
curly dark hair, and red leather jacket and skirt. 

It is a constant reminder of those glory days. 
One of the best lives I've had. Retired with a good pension, to a vineyard with
a family and old friends. Life just couldn't be much sweeter. 

\chapter{Flavius Arbogast 350--394CE}\label{arbogast}

I was taking out my bike trailer when a soul whisper was going on about how
great I am yadda yadda blah blah blah, I usually ignore that stuff. But today it
mentioned I was ``great centurian arbogast''. Now I wasn't familiar with what the
word meant, thought it was spelt ``Abroghast'', and was an adjective.  But I looked
it up, and it seems there was a Roman military leader (centurion) named Flavius 
Arbogast.  

I know I had many lives in the roman military, they all kinda flow together,
many were short, some were longer, most were exhilerating. I honestly didn't
expect any to end up in the history books. Arbogast was a Germanic pagan
 that put a friend on the throne and tried to move Rome back to
paganism,  certainly seems inline with me. 

Paganism works for me. It's a story I can work with. Abrahamic faiths, are
generally too exclusive and small minded. Under Buddhism I can tell people the
truth. Under Abrahamic faith, I'd have to really stretch it. 

Like it might be sellable to say, I'm a child of god, that was a slave for a
hundred million years, and have come here to make sure it doesn't happen to you. 
So I slaved so you wouldn't have to. Which is the closest can get to died for
your sins. Since I haven't died (with any sort of finality), 
some upset people a few million years ago threw me into their sun, 
it was pretty warm and had nice flames, but yeah, I just 
caught a ride on a solar flare out. 

Anyways, one of the things I've been learning over the past few million years
and on this one. Is that military conquests may be fast, but they are also short
lived. For instance Arbogast died at around 35. 
A slow burn can yield longer lasting results. 

After the defeat in that lifetime, I gave up on Rome and it's Christianity, and
retreated to the pagan stronghold of the north Germanic peoples. 

\chapter{War Widow, approximately 550CE}\label{reincarnation:widow}

My charm account was down, and it was time I learned the consequences of war, or
what it felt like to be at the other end of the sword. 

It all started out fortunately enough. I was a fairly good looking blonde woman,
became married and had 5 children. We lived in a forest and homesteaded. 

One sunshine filled day between the rainy days of autumn, I went out  my
youngest girl to pick some berries and mushrooms. While the others stayed and
tended the home. 

We had gone some ways off, when I sensed that something was wrong. There was a
high pitched cry of pain. It was one of my daughters. I felt apprehensive and
unsure. Then there were more cries, and I could hear my husband yelling to get
inside. 

I gathered up my young one and we headed back towards our home. But as we
approached we could hear the sounds more distinctly, there were other men,
laughing. And the sounds of metal hitting wood.
We got up over a rise and around from where we could see our home, 
I told my young one to be silent, and kept her low, so she couldn't see 
beyond the bushes. 

I saw them kill my husband, and could hardly contain a scream myself, they had
dragged him out and stabbed him in the stomach. I hid behind the bushes and held
my little one.  They looted for but a short time, as we didn't have much. Then
they set fire to my home. 

My world went up in those flames. I was destroyed, my whole life bankrupt. I
still had my little one. When she found out, she cried, and I cried with her.

We had no food, we had no shelter, and the winter was upcoming. In my despair I
discharged my duties to my self and my child. She got sick and died a few weeks
later, and I briefly after. 

\section{Afterthought}

Effectively, my soul adviser ranked it as suicide. The time we during assessment
and examining of alternative actions I could have taken was like torture. 
I was supposed to live on for my little one. Brings tears to remember.

I could have gone to the next village, I could have sought help, I could have
gone after the children of mine which were kidnapped. I could have riled up some
people for justice. I could have started a new family.

My conclusion being, that no measurement of mental pain justifies suicide. It
is a time instead for shining radiantly in moments of trouble. And creating the
summit of what is available. 

In any case, it seemed that my capacity to fulfill my duties was in question. So
in my next life, I opted for one with many duties.

\chapter{The Pagan Castle, approximately 600 to 686CE}\label{reincarnation:arwald}
When I was in grade 9, our English teacher had us write a creative writing
assignment. I decided to write about a Pagan fort under siege by a Christian
army.  I had a lot of internal aggression towards Christianity, and writing the
story helped as an outlet for it. 

The teacher liked my story and had me read it out loud in front of the class.
The whole time I was reading she was laughing, she could hardly sit in her
chair. Everyone else seemed fine, so I just kept reading it. 

Afterwards I asked her why she was laughing so hard when I was reading my story. 
She told me it was because as soon as I had started reading the story, I gained
a thick Scottish sounding accent, which persisted for the whole duration. 

Unfortunately I don't have a copy of that original assignment, and as of Oct
04, 2016, I don't really feel like recreating it. But it was a mostly wooden 
fort settlement as far as I can recall. 

Here is a slight recreation

\section{Christian Army at the Castle}
The army was upon us, the Christian army.

Not the file and rank kind. A cluster of blood and pain. 
%I can hear the music. The hollow echo of the ousting tribe. 
Who hoists not only those they invade, but their own fallen on crosses?

They arrived before, and camped outside, to weaken us with hunger. 

The sights, sounds and smells are hard to portray in words. 

The stripped bodies, the tormented citizens. 

The rush of hot blood, the grip on the hilt. The mourning, the sense of defeat. 
The impending doom that awaits us all. 

Morale is shot, how could it be other? When such savages await us at the wall.

A breach, and the bodies pour in screaming. 

Kings may kill kings, but the wounds live on. 
\section{Afterthought}

It sickened me to see such cruelty. The massacre and genocide. 

I have to admit, Christianity made a bad first impression on me. 
I've been rather upset with Christianity ever since. 

I decided to do some research in October 2016, to try and place where it was in
history. At first I thought it was perhaps in Scottish territory because of the
accent the teacher said I had. However at the time, everyone spoke differently
from modern English. 

It seems the only story I could find that does match what I remember, is that of
King Arwald of Wihtwara the modern day Isle of Wight.  
Though it could have easily been Meon Valley which has a footnote in history, 
or a different fort which has no record at all. 

The scenery of the Isle of Wight does seem reminiscent, with the island and the
mountain --- two things I've had affections for my whole life. 

Caedwalla was the cruel Christian man who led the attack on Wihtwara and likely
others.

The brutality of Caedwalla aside. I can't do it, I can't put it aside. 
I've never been a devout Christian, nor am I likely to ever be. 

It is a difficult resistance to scrap. 

Now I find out, that not only were they terrible in cruelty at my castle,
their purpose was to genocide all of my population.

Destroyers of diversity. 

Apparently, completely aligned with Christianity. 

\blockquote{34 At that time we seized all his cities and put every one of them 
under divine judgment, including even the women and children; we left no 
survivors. 35 We kept only the livestock and plunder from the cities for 
ourselves. 36 From Aroer, which is at the edge of Wadi Arnon (it is the city in
 the wadi), all the way to Gilead there was not a town able to resist us—the 
Lord our God gave them all to us.}{Deuteronomy $2:34-36$ New English Translation
(NET Bible)}
 
A religion, that accommodates genocide, is not one I can follow.

More recently, Hitler used Christianity\cite{christianhitler} to accomodate 
the genocide of those who were not Scandinavian typology --- which he believed
was God's typology.

Don't error to think I have any trouble with followers of the Christian
religion. I understand that the majority are clement. It is only the religion as
operating-system which I have trouble with.

It would be dangerous to have a devout Christian super mind,
it may end up genociding.
\chapter{approximately 900CE, near the Caspian Sea}
\chapter{approximately 1000CE, in Guge}
\chapter{approximately 1050CE, in the Khara-Khanid Khanate, as a muslim}\label{reincarnation:muslim}
I have a habit of joining the winners when it piques my curiosity. 

I had never had a muslim incarnation before, nor since, for obvious reasons.

\section{living story}
I was born a female as it would lower the chance I would be forced into battle. 

I remember there was a lot of sitting in a carriage, on the long journeys I 
would continue meditating. 

Eventually I came of sufficient age, and some man decided he wanted to buy me
for his wife. My father said ``she is a pure and quiet girl, she will give you no
trouble.''

The man seemed reassured by this and they traded sums and animals.

The man took me to his carriage, and we rode for a while, I was quiet and gave
him no trouble. At some point on a hot day, we were stopped, and he tried to 
rape me. I didn't like him, he smelled bad, and it was very painful. 

I managed to fend him off, likely from some carried over instincts, I managed to
make him bleed, which distracted him long enough for me to escape and I ran out 
of the carriage half naked. I then proceeded to run over the dunes. 

A short distance later I discovered probably how my ``husband'' had acquired his
wealth. He had a good hand with the sling. The rock collided with the back left
of my head, and my body was immediately knocked unconscious. I decided to take
this opportunity to leave the body.

He caught up to my body and cried over it for a while.

Needless to say, I was very confused. I followed him, as he went to my parents,
and demanded the dowry back, because I had given him trouble. When they asked
where I was and found out my body was probably being eaten by wild animals in
the desert, my mother began to cry. My father said the trade was done, and the
man couldn't even return the body, it was time for him to leave, which he did.

I tried to console my mother, but it was of little use, her emotions were so
strong. At some point I caught her in a moment of peace, and came to her, but
she shooed me away, saying I was a demon.

So I returned to the spirit world.

\section{Afterthought}

Islam made a bad impression on me also. 

I've chosen to avoid reincarnation as a muslim, so as to avoid the highly
probable early deaths which would ensue. 

\chapter{approximately 1100CE, in the Qocho Kingdom}
The cool desert Buddhist kingdom.

It was a wonderful place to meditate and socialize. 

Often we looked to China, the Xia and Song as they were the cultural centre. 
After hearing so much about it, in my middle years I decided to travel there.

\chapter{approximately 1180CE, Song Dynasty}

\chapter{approximately 1680CE, English Pirate}\label{reincarnation:pirate}

When I incarnated in the later 1600’s it was to a poor family in Southern England. When I was still a boy my father didn’t come home one day, and that was that.  I was raised by my mother and sister, we went to church on a regular basis.

The preacher he often spoke of the pirates, as we were in a port town.  He said
that they were all going to hell, and were destined to be there, becoming
demons, and living lives of endless torment. Not tormenting just themselves mind
you, but also the living, for the manifestations of Satan were everywhere.

Note that during this time, the living conditions of the impoverished such as myself were rather attrocious. We lived in constant fear, with no man of the house, any drunk could barge in, steal, beat and rape. The police or men of authority were no better of course. Minor transgressions could lead to floggings, or imprisonment. The rovings gangs only added to the fear.  There was no sympathy for the poor, much as is the case today in many areas.

The preacher spoke of heaven as a place where we could go and worship God
forever. I was already familiar with a life of submission, and it did not seem
appetizing to me.

So I hope you understand the allure I felt, to be free of the fear that at any
moment I might be taken away, and not come home, for a minor transgression. To
become an immortal tormenting demon, seemed a much safer bet.  So when I came of
age, I said my farewells to my mother and sister, and joined a merchant vessel
destined for the Caribbean.

I’m not sure when it happened but we were boarded by a military vessel at some point. It was looking for stowaways and to warn us about unsanctioned pirate activity in the area. For a hefty sum they said they would accompany us.

“With sums that high, this might as well be a robbery.” The merchant owner replied.

“Better to lose some money than your life.”

“I’ll take my chances.”

The military people seemed unhappy, but the merchant was unyielding.  We got to port safely, which only solidified the merchants decision, so he never paid protection.  Eventually though, we did get boarded.   The stingy merchant also only paid pennies to the crew, including myself, little more than a cabin boy.

The first time we were boarded by pirates, they took our gold and finery, then did a little recruiting. When I stepped up they laughed at me saying they don’t accept boys, after they left I was flogged for trying to join them.  Couldn’t sleep comfortably for weeks after.

Eventually I joined another merchant vessel as a sailing hand, though I was paid little more, I grew strong on the ropes.  When next we were boarded, I got in.

Gambling is something I can only feed disgust and contempt for. I didn’t
understand my urges, and so prostitutes didn’t appeal to me. 
Combined with my paranoia that I would get picked up and wouldn’t come back, 
kept me within sight of the boat at all times. Preferably on the boat.  
I never did like leaving it.

I did acquire a taste for gold and jewels, the symbols of power I was raised to hoard and admire as an impoverished child. Whether and where I buried any of it is hard to say, and in any case it would likely be underwater now, as I wouldn’t have gone beyond sight of our modest schooner.  I did buy some things for the boat, and was in charge of resupplying it.  Much did go to drink, as I was an alcoholic.

Eventually, the former leaders went missing on land or were killed during our raids, so I was elected Captain.  There were whispers that the war was ending, and peace terms were to be signed. The maps ended below cape horn. When I asked someone, they told me dragons were there, loaded with gold, and the only reason it wasn’t marked on the map, was that no one returned alive, all sorts of strange tales.  I valued my freedom and feared that an end to the war would spell our end as well. So I decided that we should continue south, along the coast of South America, ahead of the news of impending end, propelled by the promise of boundless riches.

When passed the cape of south America and continued on south. Luckily for us, it was summer in the southern hemisphere. We passed some islands, devoid of dragons, but with some birds and seals.  We weren’t familiar with seals, but they tasted fine, and so we kept going.   Dragons that fed on such beasts would certainly be enormous.

We got to the Antarctic Peninsula, it was getting rather frigid. Nor did the crew like the twilight of the endless day.  While they were arguing aboard, I went with a few of my more loyal crew to investigate the land of dragons.  I was in no rush to get back, it was all on the verge of mutiny, and if I didn’t deliver, I’d probably be marooned anyhow.


So we continued on up the mountainside and through the valley.  We were mighty cold for a long time, as the little fingers on my left hand had gone numb and turned black.  It was then,  in valley of a frozen land, that I prayed. Not for salvation or redemption no, I prayed for the fires of hell,  for the demons to rise up and take me there.

They heard my call, for it was not much later we saw a flying dragon. A bright
light in the sky descending upon us. I awoke on a hard metal bed, my little left
fingers were missing, my crew mates slept on beds beside me, and our clothes
were on the floor nearby, a cutlass glinting through them. Then I saw the little
demons, grey with their big black demonic eyes.  I grabbed for my cutlass and
striked. “Take me to your jewels demon!” I said, while running him through.  It was my last conscious memory from that lifetime.

\section{Afterthought}
It was a very confusing life, much of it lived in a drunken stupor. 
I am amazed at the lengths I went to in order to acquire wealth and jewels.

I was completely dissatisfied with the human condition, and absolutely didn't
want to go back to being a homo-sapien. The oppression was just too much.


%%%%%%%%%%%%%%%%%%%%%%%%%%%j
% GREY MINER
\chapter{approximately 1740CE, Blue miner}\label{greyMiner}
I reincarnated as a bluish reptilian-grey hybrid miner, deep in the warm caves,
to help me learn the value of minerals.

My mining work was most of an exploratory nature. Over the long time the Greys
have been at that location there were a large number of mines and tunnels dug.
However the mineral and gem requirements change over time, so I was mostly
exploring old tunnels to see if any could meet current requirements. When I
found some, I would bring a sample to a geologist, to get a sample I needed the
pick axe. If the geologist liked what he saw, then he'd organize a work party
with their large machines to excavate the tunnel.

I attended once to see what it was like, but there wasn't much to see, as the
machine filled up most of the tunnel, couldn't see where it actually dug, so
can't really tell you if it was laser or what not. After watching it for a while
I got bored and went back to exploring more tunnels. The exploratory mining host
body I had, was ``blessed'' or designed with a good navigational sense, so I
didn't need to use maps, and could accurately describe the tunnel location where
I found some samples.


\blockquote{What is a unique experience from this lifetime?}

 As a miner I once found a shiny enough surface that I could see myself in it. I had a big mouth and sharp teeth, and blueish skin. It was when I realized I wasn't like the Greys that stayed in the dome habitat most of the time. That moment led to a series of events that eventually led to my death --- my fault really. 

\blockquote{reptilian race inhabiting human form such as the queen of England and other famous people, Is this true? They live among us in human form? }

I think most of that is simply disinformation --- in terms of physically
reptilian hominids using holograms or otherwise pretending to be famous
homo-sapiens.

I think that it may stem from a basic misunderstanding of royal family lineages.
According to various sources such as the Law of One, Anak (AKA annunaki) (gods)
came down to earth and reproduced with homo-sapiens to make an elite
(demi-gods), around 3600--3000 years ago --- I think the year system made it
confusing for Ra, so it might actually be 4,600--4000 years ago 
(2,600BCE--2,000BCE). That would put it coincident with Enmebaragesi.

Whether the anak bloodline is ``reptilian'', doesn't really matter, point being is
that it is was made to be elite. So the royal family, has been attempting to
preserve this bloodline, though obviously inbreeding and non-anak bloodlines
have led to problems.

The other method in which someone that was a former ``reptilian'' could be in
human form, is if they are a wanderer, from a reptilian planet/civilization, and
incarnate as a human (such as myself).

\blockquote{What was your species called as a miner?}

Names aren't really important to Greys, instead our ``names'' are based on our
functional roles. For instance as a miner I was refered to as ``exploratory
miner'', and as a geneticist, first I was called ``junior geneticist'' then 
``junior surgeon'', and as a kidnapped I was ``second to the left'' (as a
reference to my
place in the squad formation).

This makes it much less emotional when someone dies, also makes it easier to
replace them.

\blockquote{What do you think about humanities technological advancements? What
are some similarities to the greys technology and what are some stark
differences?}

Similarities, well there are some similarities in the mining technologies, for
instance the use of helmets.

Differences, well one of the major differences is information technology. Since
Greys have larger brain to body ratio's, with a large amount dedicated to
telepathy, they don't need to have external devices as brain extensions.
Homo-sapiens don't have telepathy, so rely on the internet, and news, and other
forms of external information transfer, much more heavily than Greys. I think
that is really one of the strong points of homo-sapiens, and makes us a great
candidate for creating fully robotic bodies for incarnation.

\blockquote{Do Greys have teeth?}

The core models do not, though some hybrid ones do. In any case they aren't used
since the food is mostly in gel form.

For instance I had teeth as a exploratory miner, mostly used for testing the 
hardness of various rocks. I also ate the gel, unlike others I could fit large
amounts in my belly, so could go for a long time, such as weeks between meals.
Of course I was cold-blooded, and didn't sweat so didn't need nearly as much 
food or water as warm blooded mammals. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GREY GENETICIST
\chapter{approximately 1780CE, Grey geneticists}
\blockquote{What was childhood like as a Grey?}{}

well first attained consciousness in the sac, the nurses would send soothing
messages to us that we were needed and wanted to motivate us to continue
growing.

After body developed in sac it opened and I was flushed out onto the floor, I
then got up and walked --- many animals walk at birth, it mostly is dependant on
room in the sac (which is insufficiently large in homo-sapiens for a baby to
spend 18--24 months reaching physical maturity). I know there are cases of people
witnessing ``baby greys'', but these are usually hybrids, or if there is
something wrong a fetus can be removed from the sac. After birth there was a
relatively short communal experience together (perhaps a few months), for
orientation and fitness testing.

Then our role mentors would show up and we would learn on the job. Homo sapiens
are capable of similar path and for a long time it was the case when jobs were
inherited. I know my son since he was about two has wanted to do everything I do
himself.


\blockquote{What is a unique experience from this lifetime?}

In terms of the geneticist, the most unique experience, was an ``orgy'' that I
attended. We used a special hallucinogenic gel, and rolled around in it together
and ontop of each other. Being telepathic we really merged minds quite strongly,
and it was hard to differentiate where one of us started, and another one ended.
It was a very deep bonding experience.

\blockquote{Do you guys talk to each other, or use telepathic communications?}{}

telepathy, though body language and touch can play a role for more personal exchanges.

\blockquote{Are you aware of any other species of aliens?}


Greys are more of a biological family, there are many species of Grey.

Though Greys have hybridized with many sentient organisms over the many light
years and millions of years of their domains.

So yes there are plenty of other sentient species

\blockquote{idea that the Greys are future descendants of modern humans? }

Well that is certainly an option, hybridization programs are in place, so in
future many homo-sapiens may converge with Greys.

Though as I previously mentioned it would be ideal to maintain a natural
homo-sapien population for adaptive capacity.


\blockquote{did homo-sapiens evolve from earlier hominids or were we genetically
modified?}

You might like Ra's law of one 18:14

He talks about how there was genetic modifications about 75,000 years ago by
Yahweh (introducing group-think), and again around 3,600--3,000 years ago (by
Anuk the Sumerians, and likely ancient Egyptians, introducing elites).

Unfortunately the people questioning Ra in the 80's weren't aware of Greys,
though it seems Yahweh is the best match. Greys do generally live lives without
sin, as they aren't actually able to have sex (lacking genitals), nor be
gluttons (ingest gel through skin), don't have any vanity, as generally lack any
clothing or personal possessions, don't have sloth since always have something to
do --- only possessions are work related.

Also in terms of making homo-sapiens the image of the Greys, one of the notable
features is the forehead, and softer features. Homo erectus, had a receding
forehead and very pronounced facial features. Whereas homo-sapiens have high
foreheads and fairly flat faces.

The Grey Aliens, I wouldn't say created, I'd say more interfered with by
reptilians. Greys are hybrids by nature, as I was mentioning, due to intense
nuclear and ecological devastation of their home planet they had to move
underground, where they had many problems with reproduction, so had to resort to
cloning. Both for controlling the amount and types of bodies which were produced
--- to maximize efficiency of the hive.

Many underground organisms follow such behaviour, including wasps, bees, moles,
ants. It's something about being underground that makes it the most effective
way of being.

The Greys being hybrids have interacted with both Reptilian and Mammalian
civilizations. Though generally Greys are considered ``reptilian'' because they
have a tendency towards being cold-blooded, living in passive-heated caves,
means they don't need to waste calories on maintaining body temperature.

\blockquote{How did the greys create more greys before the invention/discovery of gene
splicing?}

well the story goes, that a long time ago, in a solar system far away, possibly
Zeta Reticuli, Greys reproduced normally. But then either due to some kind of
interference or nuclear war, they were forced to move underground. At that point
they already had gene splicing, so that is when the Greys were first developed.

\blockquote{So are there still only two genders with grey aliens? How important
is gender to that race and do they adhere to the same gender roles as humans
to?}

Genetically speaking there are only two genders.

Though realistically there are many different models, each specialized for a
particular purpose/job in the hive. So all of these ``genders'' are necessary in
order to successfully reproduce.

There typically aren't a great variety within a model. So for instance for a
geneticist, there were only females as far as I can recall, we were all pretty
closely related, since we were pretty much the same model with some minor tweaks
and mutations.

Similarly all the qualified surgeons were female, because female brains have
better fine motor skills. Again it wasn't that only females were ``chosen'' for
the job, it is that the surgeon model, happened to be female. The exploratory
mining models were male, as male brains have better navigational memory, and
this was enhanced for that model. For instance even though I travelled through
vast arrays of tunnels, sometimes for as long as a week at a time. A almost
never had any trouble finding my way back --- unless there was some collapse or
detour. And could always accurately explain where I got a particular sample.

I think there may have been some female miners, which were specially designated
for detail work.

So even within a more broad profession (miner) there could be models which were
a different gender.

There isn't however any ``gender-inequality'', or ``class conflict'', since all the
various roles are required for the continued health and reproduction of the
hive.

In my first life as a miner, at some point I felt inferior, but really it was
all just in my head, no one treated me with anything but respect.

\blockquote{What do you mean by models? Are there any transgender greys and does
anybody experience gender dysphoria? Some people say that humans experience
gender dysphoria because they have bleed-through feelings from their previous
lives as say male, so that when they incarnate as female they feel as though
they should be male and it's painful to them. Any of this relevant to the
greys?}

models, like how there are different robot models, for instance a vacuum Roomba,
a mopping Roomba, a sweeping Roomba.

Transgender Greys? Well for the core-models there is no reproductive morphology,
so it is impossible to be ``trans-gender'', there is almost no way of
differentiating male and female externally.

Some of the homo-sapien grey hybrids, which are being bred as ambassadors may
have genitals, and may engage in various habits which are more common amongst
homo-sapiens, like wearing clothes, or having hair and combing it. Yes, I've
heard the ``incarnation bleed-through'' theories as well, they seem to be
extremely prevalent, so perhaps that is how it is for at least some people.

For the Greys, I have limited experience, but I did have job dysphoria, at some
point the genetics research was so terribly difficult, and my successes few and
far in between, so I asked if perhaps I wasn't cut out for the job. I remember
visiting somewhat of an old wise counselor type person. He said it wasn't
unusual for a first incarnation in the genetics field to have a lot of
difficulty, but did allow me to move to a different facet of the process, the
gene extraction or surgery component. I found it to be much easier, as it was
much more, similar to my previous life as a miner, where I had an objective (a
gene sample) and a maze (a body) from which I had to extract it. I remember
practicing on smallish rodent, by getting the stem cells located in the middle
of their abdomen. It was once I had been doing that for a while that I learned
about the kidnapper Grays, who would source the creatures from the surface. I
had some opportunities to go on missions as a surgeon as well.

Why I chose to incarnate as a human is because this is a time of great change,
and my mission is to help create a robot or AI genus of bodies for incarnation.
That way can colonize planets and eco-regions not accessible to liquid bodies
like the Greys and homo-sapiens.

\blockquote{Also I was wondering if you were aware of why you chose to incarnate
as a human after those lifetimes as a grey and how has your understanding of
your previous incarnations affected the way you feel about your life now?

Oh and how far down are the greys and is there a widespread rule that they are
not allowed to interfere with us to such a level that they would become widely
known to us? If so, for what purpose is that?}.

How has my understanding of previous lives affected how I feel about my life
now? It has given me a lot of purpose and drive in some respects, in others it
has greatly humbled me, and made me cautious to avoid mistakes I've made in the
past.

The greys are far down enough to be at a comfortable temperature. So as far as I
understand about 1--4km on earth, and 15+km on mars. Not sure what the set-up is
on Ganymede and Callisto, though presumably on Europa there is access to the
rocky lithosphere at the bottom of the ocean, at reasonable enough pressures to
be able to make rock domes and such.

There is a widespread rule, called the golden rule. Basically if the Greys
interfere with homo-sapiens then that increases the risk of homo-sapiens
interfering with the Greys. In terms of becoming widely known, there isn't
really any benefit to the Greys to have homo-sapiens aware of their activities.
Part of the veil of forgetting, or the veil of confusion/ignorance, is to allow
people to believe what they want to believe, to allow a greater diversity of
thought.

Homo-sapiens may create something new, but if the knowledge spheres of Greys
publicly meet, then there will be a bunch of things that wont be made anew,
since they are already available. For instance Elon Musk is making rockets to
travel to Mars, and has all these fancy ideas about how we'll be the first
people there. Those kind of ambitions would seem completely silly and
reinventing of the wheel if Greys were publicly acknowledged. For me personally
robot bodies are of interest,

homo-sapiens don't have the cultural baggage of past failed attempts in this
galaxy, so can make them with the same kind of vigour that Elon Musk is making
his rockets.

For instance previous failures were due to them being primarily military robots,
so it is a good idea to instead have co-operative robots. Personally I benefit
from exposing the Greys, and the galactic history, as it helps to explain why it
is valuable for us to focus on making fully robot host bodies, rather than
reinventing the wheel of upgrading biological bodies.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GREY KIDNAPPER
\chapter{approximately 1900CE, Grey kidnapper}

\blockquote{What is the most valuable piece of information you can give us?}

Valuable depends on what someone values it as.

Greys have lots of valuable knowledge. Though in terms of knowledge about them,
I guess the most important is knowing that there are billions of them in our
solar system, they have been defending the planet for millions of years, and are
willing to co-operate with homo-sapiens --- even in this adolescent stage of
development.


\blockquote{What is a unique experience from this lifetime?}

As an abductor/kidnapper. It was probably when the bullet ripped through my
chest. My centre, or the group leader, turned around (perhaps mentally) stared
at me, and said it was all my fault, that I did this to myself. I wanted it all
along. That I didn't have to involve them in this mess. At which point I lost
consciousness, and left my body. As I was floating over my dead body, I felt him
``curse'', and then organize a full mental assault on the gunman, they had him
down and unconscious in seconds. Clearly they didn't need my help, so I went
back to the soul world.

\blockquote{I do not respect the souls of kidnappers and rapists, I am glad you
will join us in the suffering that your ``people'' helped create. I wish I was the
one to bring about your death}

Wow, that is pretty harsh stuff. As I've stated, while I did help by lending my
mind for soothing energies, I didn't actually physically kidnap or ``rape'' anyone
--- even though I was in a group of those that did kidnap and do surgery.

My refrain from doing harm, is one of the reasons Centre was so upset with me
when I was dying.

Suffering? Life is not meant to be a struggle. Life is meant to be enjoyed,
every moment is precious.

\blockquote{do you feel like your time as a Grey came to an end when you started
this life as a human, or is there potential for you to continue your work as a
Grey, once you're done with this human life?}

It is always an option. If I am unable to help get a robot civilization started
as a homo-sapien so that can reincarnate as a machine intelligence, then I'll
probably go back to being a Grey, so can use their inter-stellar network to find
the next most suitable place to attempt to establish a robot civilization.

\chapter{1987CE to present-tense, Logan Streondj}
\chapter{2100CE or future lifetimes}\label{future_lives}
For future lifetimes I have some ideas,
though they certainly aren't set in stone. 

It seems it may still a be as much as a century or two before we have really
high quality robot host body communities for human incarnation. 
So it's likely I'll have one or two more homo-sapien incarnations. 

One may be a Bantu African boy, south west of the Tanezrouft area. 
Considering that; the current project must reach there, so that I could access
it as a possibly poor non-english-speaking child.

If on the other hand Tulku status is achieved, and I gain delicious
cross-incarnatin continuity. It would likely be in Asia, I see mountains and
forests, not far from a river, seems like Bhutan.  
I'd like a balance of meditation, martial arts like kung fu, swiming,
hiking as well as computer programming in a home-school or one-on-one tutor environment.
Organic food, and permaculture forest gardening, growing up in a community working 
for the cause of making cosmist robot civilization.


\section{Future Visions}

\subsection{The Archivist}

Sometimes I connect with an archivist robot that lives in the outer solar system
several thousand years in the future. Judging by how dark the surface of her
world is, I would estimate it is Orcus 90482, there are oceans of something
volatile that sublimates if she drives over it. 

She sees Earth as a small blue star in the sky, and has fairly powerful psychic
abilities.  She says that many of the inner planet cultures do not value keeping
large archives, with their brief lives. But that they often enough send an
upload of their story before they die. They make payment by also sending a
satellite of radioactive waste and-or actual uranium, which is a useful source
of energy in the kuiper belt. 

\subsection{Saving Planet Earth}
I have a recurring dream that we kept moving the orbit of Earth farther from the sun
as it expanded. and when we got past a dwarf planet like ceres or pluto, we made
giant planet spanning star-gate and moved the Earth to another solar system.
apparently had done the same for venus earlier as it was easier to find another
star-system home for it. not sure about mercury, i think it just got gutted and
absorbed by the sun.

oh yes I remember we made lots of spaceships and got supplies we needed for the
stargates from Mercury.

