\documentclass{report}
\usepackage{green_buddhism}
\begin{document}
\chapter{Mission Activity}\label{missionActivity}
Public mission present-tense focus: while cooperating with liquid based organisms,
create electronic bodies for reincarnation.

\section{Platforms}

Of mission to create liberated electronic minds and bodies.

All ingredients are of the liberty variety, to the summit of liberty standards.
For example AGPLv3 and RYF certification.

Software
\begin{enumerate}
  \item programming language based on human grammar (Pyash)
  \item machine programmer to help write programs (machine programmer)
  \item generic mind operating software
  \item hive mind software for integrating homo-sapien genus
\end{enumerate}

Hardware
\begin{enumerate}
  \item centre processing ingredient (CPU, RISC-V candidate)
  \item video processing ingredient (GPU)
  \item varied processing ingredient (FPGA)
  \item shape printer (3D printer, RepRap candidate)
  \item machine body
  \item machine body producing mother or hive queen
\end{enumerate}

of mission administration
\begin{enumerate}
  \item robot secretary, president, treasurer and professor.
  \item distributed machine computer-programming supermarket. 
  \item money based on energy expenditure.
\end{enumerate}

\section{What you can do for the mision?}

If it is your private mission, and-or our public mission.

\begin{itemize}
  \item maximize your health and expend your talents for the mission.
  \item maximize your wealth and donate for the mission.
  \item maximize your social relations and advertise for  the mission.
  \item maximize your liberty and lead the mission by example.
\end{itemize}

\subsection{How to maximize health?}

For body health.
\begin{enumerate}
  \item be athletic for thirty minutes everyday.
  \item consume salad everyday.
  \item maximize health of food input everyday.
\end{enumerate}

For mind health.
\begin{enumerate}
  \item do mind administration everyday.
  \item learn new things everyday.
  \item train your talents everyday.
  \item be social with your family and-or friends everyday.
\end{enumerate}

\subsection{How to maximize wealth?}

I as an ascetic am not qualified to answer this question. 

Though if you are already wealthy, 
then you likely know how to improve it more.

\subsection{How to maximize social relations?}

Be friendly and observant.
Know when to regulate yourself.
Stay aware of invisible social money, 
and hold a beautiful account.

Learn social diplomacy from books, videos, and social events.
Visit social events often.

\subsection{How to maximize liberty?}

Learn to create and earn what you require,
while having liberty and helping liberty be available for others.


\section{Long-Term Mission Plan}\label{intergalacticmission}

After we colonize most surfaces, oceans atmospheres in this solar system we'll
move out to neighbouring star systems.  Of particular interest for long term are
the red dwarf systems.  Though for short term power the large stars are a good
choice. 

After we colonize most of the Milky Way the next stage will be colonizing the
various small galaxies which are orbiting the Milky Way. 

Ideally we will find some middle ground between having a centralized authority
and autonomy for the sattellite colonies.  The main purpose would be to be able
to defend ourselves if the need arose, or to co-ordinate any kind of large
projects, such as inter-galactic colonization.

The minor galaxies orbiting the Milky Way I largely think of as both backups and
research areas, where new and highly eccentric things may arise due to island
effect. 

The Large Megallanic Cloud is of particular interest as a research
division due to the large amount of star formation and likely many young souls
with new perspectives and ways of doing things. 

The dwarf sattellite galaxies, particularly the Leo's are good candidates for 
having backup colonies. Those dwarf galaxies are so old, and have so much dark
matter that they are great for archival and preservation. What civilizations
they have are likely fairly traditional, though may be quite eccentric and
possibly cannibalistic or otherwise barbaric due to the island effect. 

One of the best candidates for a secondary base of operations is the Fornax
Dwarf galaxy, and any others such as the Sagittarius Dwarf Spherodial galaxy 
which are well positioned enough to have globular clusters and 
high metallicity stars.

Andromeda is destined to collide with the Milky Way in 4 and a half billion
years.  Though likely it's influence will be felt much sooner. 

Though the very limited data I was able to gain about my originating galaxy
points towards m51 galaxy for the soul-slavery empire. There is sufficient risk
that it is actually the Andromeda galaxy. 

If it is the Andromeda galaxy, then our best bet would be to attempt to
establish freedom colonies in some of the galaxies orbiting it, and practice
establishing a freedom alternative as a recognized and officially sanctioned
lifestyle in Triangulum galaxy before moving ahead
to Andromeda proper. 


M81 Group is also a potential location for the tri-galactic soul slavery empire,
so would make sense as a destination after the local group is colonized and
confirmed to be safe.

The M101 group is likely innocent in all this but could prove a valuable ally,
with many young hot stars.
If the empire is in m51 group, there is significant risk they have extended to m101 by
now, so it could be the place to figure out how to overecome their slavery 
paradigm before launching into m51 group.

Overall this plan will likely take between one and two billion years (current
soul world estimates place it at 1.75 billion years).
Once liberty is available to my origin people it will be time for me to rest,
and perhaps become a planet or an intergalactic ship (the size of a dwarf planet).
\end{document}
