
\documentclass{report}
\usepackage{green_buddhism}
\begin{document}
\chapter{Origination}\label{origination}
\begin{table}
\begin{tabular}{l l} 
  no colour & black \\
  no sound & quiet \\
  no emotion & content \\
  no motion & stopped \\
  no number & zero \\
  no temperature & zero kelvin \\
  no feeling & frozen \\
\end{tabular}
\caption{Attributes of Nothing}\label{nothing}
\end{table}
\begin{enumerate}
\setcounter{enumi}{-1}
\item In the begining there was nothing (Table~\ref{nothing}). Zero.
\item Then there was Not nothing. NOT the first activity. 
\item Afterwards there was not And nothing. AND the second activity.
\item Conditional activites appeared. 
\item The base cosmos grew more complex. 
\item Geometry developed. 
\item With shapes, there were enough bodies for social experience.
\end{enumerate}

\section{Soul World}\label{soulWorld}

The soul world is in the base cosmos, or close to it.
There we with you float around as balls of light in geometric forms ---
This is verifiable via life-between-lives regression
hypnotherapy\cite{newtins}\cite{newton2000destiny}

Eventually we with you got bored of floating around in base cosmos,
and decided to create new and more complex cosmos.
After some ``time'', we with you created the galaxy cosmos, where you are reading this
text.

When we with you reincarnate in this complex galaxy cosmos, just as when you are 
playing virtual computer sports, a part of you stays in one world, and a part
of you dips into another.

\section{String Theory}

String Theory, or M-theory is a set of beautifully simple math formulas which is
also compatible the galaxy cosmos.

As Creation became more and more complex, eventually it stumbled upon string
theory, and started expanding on it, so our galaxy cosmos came about.  I say we
with you created it, because we with you are all a part of Creation, the same
Creation that created the galaxy cosmos. 

\section{Time Complexity}

On Earth time is traditionally measured by the orbital characteristics of the
planet, though measuring by atomic decay is also available. 

In Creation, `time' is measured by complexity. So if nothing happened at
complexity 0, then Not nothing happened at complexity 1, '1' happened at
complexity 2, and so on. 

Pegasus time-machine experiments show inconsistent results when sending people
multiple times to the same time/place.  

\subsection{Entropy Horizon}

If you go far ahead enough in time, then you'll inevitably come across a
cataclysmic event that makes things simpler.  This is the entropy horizon or
`bleeding edge' of the universe.   Ironically enough, if you just wait some
time, and then go back to the same time-place it may not be in a state of
cataclysm but a continuation,  because Creation has accrued enough entropy to
know how to avoid the cataclysm. 

This may be why there are many people that seemingly prophesize end-times, which
never come to pass.  Because we generally don't live at the bleeding edge, so
things have enough time to resolve themselves before we get there. 

It's not that those prophets were inaccurate, at the time-complexity they said
it in, it may have been correct, but after a certain amount of time-complexity 
passes it ceases to be correct. 

It is similar to how it is near impossible for someone to go to the future, get
a listing of historical stock prices, then go back in time and get super rich.
While it may work on a short-term time-hop, it is less likely to work the
farther ahead you go, due to the complexity changes. 

\end{document}
