
\chapter{Living in Peace}\label{peace}

The Bodhisattva commands, are followed by the most devout of Mahayana Buddhists.

Here is one that equates causing disconnect in the community with killing ones
own parents. 
\blockquote[``Bodhisattvabhumi'' section of the Yogācārabhūmi Śāstra.]{[Avoid] 
committing any of the five extremely negative actions: 
\begin{enumerate}
  \item killing one's mother, 
  \item killing one's father, 
  \item killing an arhat, 
  \item intentionally drawing blood from a Buddha or 
  \item causing schism in the community by supporting and spreading sectarian views. 
\end{enumerate}
}

This is one of the reasons that in Mahayana Buddhism, there are no ``sects'', 
rather they are schools. All the schools are teaching for the betterment of the
community, so we co-operate. 

Similarly we can be with other races, genuses and forms of life. All forms of
life are schools for the souls that inhabit them.

\blockquote[Buddhist Teachers and Leaders in the United States\cite{racial}]{Our
 collective aspiration within the Buddhist traditions is to become truly 
inclusive and beloved communities.  In this process we are committed to 
honestly and bravely uncovering the ways we create separation and 
unintentionally replicate patterns of inequity and harm.  In the same spirit, 
we are committed to engaging with other faith and social justice groups in 
support of undoing racism throughout our society.
}

In my meditations I've found that often anger I feel towards others, is actually
derived from fear and low self worth within myself. It is one of the ways I
uncovered a way I was creating ``seperation and unintentionally replicating
patterns of inequity and harm''.

Considering the trouble homo-sapiens have had with racial hate amongst their 
own genus, it is not surprising that governments and extraterrestrials do not 
think homo-sapien populations already have the capacity to form peaceful 
relations with other genuses.

I know that at moments when I felt racial stress, it was because I was
threatened by them. I was apprehensive that my family would be deleted in favour
of theirs. So it seemed to me that I should attack first. 

But there are consequences to attack.

\blockquote[Martin Luther King Jr.]{Hate begets hate; violence begets violence; 
toughness begets a greater toughness. We must meet the forces of hate with the 
power of love\ldots{} Our aim must never be to defeat or humiliate the white 
man, but to win his friendship and understanding.}

A better activity is respect. By the golden rule, if you give respect, you will
attain respect. 

I do not say love, as excess love could lower diversity. 
I say respect; giving other region to live in peace. 

The Greys live in the lithosphere, and robot or electronic body communities 
can live in regions which are not inhabitable by liquid bodies.

In this way, we can all attain living peace in our solar system, 
and galactic domain.

\section{Terms of Peaceful Trade Relations}\label{terms}

For the Greys and governments to feel safe in making public trade relations
between Greys and the homo-sapien public.
Homo-sapiens must demonstrate that they can be peaceful with each other and
friendly to the ecology of Earth.

That denotes we have to stop warring with each other,
and stop terrorizing each other.

To be violent to anyone, grows the danger that they will be violent in return.
For the population that is suppressed, tries to delete the suppressor. 

Giving education, horticulture and region of peace, and we shall attain it in
return.

For those that have religions that incentivize a violent death, let me
demonstrate the in between life experience.

\subsection{What is the reward of Jihadi's and Valhalla seekers?}
After death, at first, it is indeed what they have imagined. 
But after some time, the truth begins to slip between the cracks. 

You may be drinking with the Gods, when in the corner of your eye, you see a
woman that you killed, with an axe in her head. You look again, but she is gone.
Finally the gods are silent, and you are sitting at a table of the dead, all
those you have killed, and the gods next to you are your relatives, with sad 
eyes for your activities.

It happened to me, after a life as a varingjar. 

After you feel contrition, it can stop and the rehabilitation can begin.
Rehabilitation may include planning lives, where you will bear the pain of your
victims, or if you choose the dangerous parts of your soul will be stripped, and
you will become a scrap of the old you.\cite{newton2000destiny}

I have not been a Jihadi, but the story will be similar. Your soul family will
make a theatrical play, that moves from what you imagined, towards the mutual
truth, circumstances where you have probability to experience contrition.

Perhaps the virgins will become disfigured with the wounds of your victims, and
you will realize that the one summiting you is your mother, giving you sad eyes.

That is if you have been respectful and cooperative most of your life. 
If not, then you might be pushed to reincarnate rapidly, into a life where you
will bear much pain, so you could feel the pain of your
victims.\cite{newton1994journey}

