\part{World Religions: Operating-System Assessment}\label{worldreligions}

I will assess the varied religions for their use as a base for super minds.

I organize them based on their family.  

\chapter{Shamanism}
\chapter{Paganism}
\chapter{Hinduism}
\section{Brahmanism}
\section{Hare Krishna}
\section{Yoga}
\section{Sikh}
\section{Buddhism}\label{Buddhism}
\subsection{Theraveda}
Theraveda Buddhism may be the oldest form of Buddhism, but it is also one of the 
more dangerous ones.
For example they have a quote ``if you see a Buddha the street, kill him,
throw him in a ditch and keep walking''
This form of extreme disrespect for those who may be more knowledgeable even
caused meditation to die out in Burma.
Theraveda Buddhism is also known for oppressing people of different faiths,
which leads to conflict. As in Sri Lanka with the Hindu's and perhaps in
Thailand with the muslims. 
In part this conflict is because in Theraveda Buddhism you aren't allowed to mix
different religions together. 
\subsection{Mahayana}
Mahayana is the most popular form of Buddhism, and is far more peaceful and
respectful. Drawing the blood of a Buddha is considered a crime equivalent to
that of murdering ones parents.  The path of the Bodhisattva, the ones who live 
to help others is revered.  

Mahayana allows the mixing of religions, so accepts all faiths. 

\subsection{Vajrayana}
Vajrayana is an offshoot of Mahayana popularized on the Tibetan Plateau. 

Historically they certainly had their conflicts with Islam, which wanted to
obliterate them.  But the current Dalai Lama seems to have forgotten about it. 

Anyways, so Vajrayana is the first faith to support immortality,  or
cross-incarnation continuity.  They've developed a method of location
reincarnations of various lamas or teachers, so they could continue their
teachings over the course of several lifetimes. 

\chapter{Abrahamic}
All Abrahamic faiths that I am aware of are dangerous.

But then again, I've been genocided by Christians, slaughtered and 
stoned to death by muslims, so I'm biased. While Jews haven't done anything
unfavorable to me, the Torah supports genocide.

While I don't hold a grudge, I'm extremely wary --- avoiding death makes sense to
me. 


\section{Judaism}
One of the cardinal trouble with Judaism, and thus all the Abrahamic faiths
(Christianity and Islam), is that
it explicitly accommodates genocide and holy war. 

\blockquote{18 (17) Thou shalt not allow a mekhashefah (witch, sorceress) to
live.}{Shemot 22:18Orthodox Jewish Bible (OJB)}

This is a command to genocide ancestor religions.
The children religions of Judaism genocide Jews similarly.

This line was used by Christianity to form the Inquisitions, which sabotaged
feminine authority anywhere it appeared. 

\blockquote{24 For I will drive out the Goyim before thee, and enlarge thy borders; 
neither shall any man covet thy land, when thou shalt go up to appear before 
Hashem Eloheicha shalosh in the shanah.
}{Shemot 34:24Orthodox Jewish Bible (OJB)}

Goyim are non-Jews.  Since Judaism is generally only inherited, it accomodates 
the genocide of all non-believers. As seen in the following text:

\blockquote{34 And we took all his towns at that time, and in cherem utterly
destroyed them, and of the nashim, and the little ones, of every town, we left
no remnant;
35 Only the behemah we took for booty unto ourselves, and the plunder of the
towns which we took.
36 From Aroer, which is on the edge of Wadi Arnon, and from the town that is by
the wadi, even unto Gil‘ad, there was not one town too strong for us; Hashem
Eloheinu delivered all unto us:
} {Devarim $2:34-36$ Orthodox Jewish Bible (OJB)}

\blockquote{34 We captured all the cities that belonged to King Sihon at that time. We
completely destroyed the people in every city—the men, women, and children. We
did not leave anyone alive! 35 We took only the cattle and the valuable things
from those cities. 36 We defeated the town of Aroer on the edge of the Arnon
Valley and the other town in the middle of that valley. The Lord let us defeat
all the cities between the Arnon Valley and Gilead. No city was too strong for
us. 
}{Deuteronomy $2:34-3$ Easy-to-Read Version (ERV)}

\blockquote{3 Now go fight against the Amalekites. You must completely destroy the
Amalekites and everything that belongs to them. Don’t let anything live; you
must kill all the men and women and all of their children and little babies. You
must kill all of their cattle and sheep and all of their camels and donkeys.’”}
{1 Samuel 15:3Easy-to-Read Version (ERV)}

\blockquote{Pour burning coals on their heads.
    Throw them into the fire.
    Throw them into pits they can never escape.
}{Psalm 140:10Easy-to-Read Version (ERV)}

It would thus be dangerous to have a Judaic super mind, 
as it try to genocide all non-Jews. 

Ironically Hitler may have used those same texts to justify his genocide of the
Jews --- because he was a Christian, and it includes the Old Testament. For
instance many were incinerated, as the Psalm calls for. 

\chapter{Christianity}
Jesus arose on the tail end of the Ptolemic Kingdom, 
which had plenty of Buddhists.  

So the similarities between Buddhism and Christianity,
could be ascribed to him having studied with some Buddhists who lived in the
area. 

In fact some of the most Buddhist places in the Ptolemic kingdom,
 became Christian there after. 

However the majority of his time, he probably spent studying Judaism.

The bits of Buddhism that Jesus seems to have taught, or at least the
parts of it that were recorded were strongly distorted, and so even the New
Testament has violence and hate.

\blockquote{12 But the unfaithful heirs of that kingdom will be thrown into
the darkness outside. In that place there will be wailing and gnashing of
teeth.”
} {Matthew 8:12 International Standard Version (ISV)}

There is some speculation that Hitler used this line to justify genociding
the Jews. Using the Old Testament as a guide for how to go about it.

\blockquote{23 And anyone who refuses to obey that prophet will die separated
from God’s people.’[a] }{Acts 3:23 Easy-to-Read Version (ERV)}

This line has been used to destroy countless of ``heathen'' cultures and people,
 reducing diversity both culturally and genetically. 

A common tactic that was used, was to at first offer a bible, and if the people
did not switch to Christianity, then they were destroyed.  This happened for 
instance on the Isle of Wight, and in South America.

In conclusion, Christianity also accommodates genocide and holy war,  pushing it
a little bit farther than Judaism. Thus it would be dangerous for a super mind
to have this religion as an operating-system. 

\section{Islam}
\subsection{Caliphate}
Caliphate Islam, includes Sunni, Shiite and several others,  all directly
descendant from Mohammad in one way or another, via a succession of Imams. 

It is the main kind which has been spreading through violence, both to
non-believers and believers alike. 

Of all the faiths, this sort should be avoided the most as a basis for super
minds.  Since it may genocide not only all non-muslims, but also all
homo-sapiens --- via the tafkir justification that homo-sapiens aren't as good at
following Islam as a robot mind. 

\subsection{Sufi}

Sufi Islam, doesn't really regard the Quran very much,
it also says that the holy war is in the mind. 

Now while this is safer than the Caliphate forms of outward physical violence. 
I wonder if it may accomodate cyber attacks, and other forms of ``mind'' based
holy war. 

So to be on the safe side, it is best to avoid it as a super mind
operating-system.

\subsection{Bahai}

Bahai says all mentions of holy war are to be stricken out from the Quran. 
So in that sense, it may be at least safe to a degree.
\subsection{Conclusion}
\chapter{Humanism}
\chapter{Materialism}
